Thesis Title

### 2022-11-04 chapters/acknowledgements.tex
finish first draft of the thank you section

>>>>

To the friends I made in the Netherlands, Casper, Lieke, Boas, and whom I had the pleasure of sharing a fantastic and dynamic workspace with, Erley, Nilay, Peppe, Leo and Natacha, my biggest thanks. You made my adventure of living abroad memorable.

To my friends who have become more than family, Nuno, Alicia, Sofia, Neto, Margarida, thank you for being there in my lowest and highest moments. I'm blessed to have you in my life. To you, Rúben, who grew from a little pebble in my shoe to a huge rock for me to lie against, thank you.

To my mum and dad, thank you for your unconditional love, for being my biggest fans, my most loyal allies. To my sister, who never fails to push me to be better, you're my best friend in the whole world. To Miguel e Inês, you bring so much joy to my life. Being your aunt is not only a pleasure, it's an honour to be able to watch you grow. Even though work has made me miss many birthdays over the years... To my brother in law Nuno, thank you for showing me what perseverance means. To my grandma, who is more than a mother to me, and my grandpa, who might not be here anymore but will live forever in my heart, thank you for showing me what love means, now and forever. To you, my dear grandpa, I dedicate my life's work, to honour you and your memory every day of my life. O primeiro bebe-se inteiro.
